---
title: "Test with a new {dplyr} version"
description: |
  Rendering a post using a {renv} profile with {dplyr} version 1.0.8.
author:
  - name: Matt Dray
date: 2022-03-14
output:
  distill::distill_article:
    self_contained: false
---

# Set up

To generate this demo, I:

1. Created this new post
1. Activated a {renv} profile with a unique name
1. Installed the packages needed for the post
1. Captured the dependencies in the profile's lockfile

```{r eval=FALSE}
distill::create_post("dplyr-108")

renv::activate(profile = "2022-03-14-dplyr-108")

renv::install(
  "distill",
  "rmarkdown",
  "palmerpenguins",
  "dplyr@1.0.8"
)

renv::snapshot()
```

To demonstrate package dependency control, I've installed {dplyr} version 1.0.8 for this post, which is the current version and includes the `across()` function [introduced in version 1.0.0](https://dplyr.tidyverse.org/news/index.html#across-1-0-0).

I've written another post that uses an older version (0.8.5) of {dplyr} to prove that the dependencies don't conflict.

# Proof

We can prove the `across()` function exists for the version of {dplyr} installed with the '2022-03-14-dplyr-108' profile.

```{r warning=FALSE}
suppressPackageStartupMessages(library(dplyr))
packageVersion("dplyr")
any(grepl("across", ls("package:dplyr")))
```

# Demo

This means we can use `across()`, rather than {dplyr}'s old approach of the `*_if()`, `*_at()` and `*_all()` variants of verbs like `mutate()` and `summarise()`.

Here's a very small example.

```{r}
palmerpenguins::penguins %>% 
  select(where(is.factor)) %>% 
  mutate(across(c(species, island), tolower)) %>% 
  head()
```
