---
title: "Test with an old {dplyr} version"
description: |
  Rendering a post using a {renv} profile with {dplyr} version 0.8.5.
author:
  - name: Matt Dray
date: 2022-03-14
output:
  distill::distill_article:
    self_contained: false
---

# Set up

To generate this demo, I:

1. Created this new post
1. Activated a {renv} profile with a unique name
1. Installed the packages needed for the post
1. Captured the dependencies in the profile's lockfile

```{r eval=FALSE}
distill::create_post("dplyr-085")

renv::activate(profile = "2022-03-14-dplyr-085")

renv::install(
  "distill",
  "rmarkdown",
  "palmerpenguins",
  "dplyr@0.8.5"
)

renv::snapshot()
```

To demonstrate package dependency control, I've installed {dplyr} version 0.8.5 for this post, which is the version [before the `across()` function was introduced](https://dplyr.tidyverse.org/news/index.html#across-1-0-0).

I've written another post that uses a newer version (1.0.8) of {dplyr} to prove that the dependencies don't conflict.

# Proof

We can prove the `across()` function doesn't exist for the version of {dplyr} installed with the '2022-03-14-dplyr-085' profile.

```{r}
suppressPackageStartupMessages(library(dplyr))
packageVersion("dplyr")
any(grepl("across", ls("package:dplyr")))
```

# Demo

This means we have to make do with {dplyr}'s old functionality for `across()`, which amounts to the `*_if()`, `*_at()` and `*_all()` variants of verbs like `mutate()` and `summarise()`.

Here's a very small example.

```{r}
palmerpenguins::penguins %>% 
  select_if(is.factor) %>% 
  mutate_at(vars(species, island), tolower) %>% 
  head()
```
